Neural Networks for Neural Tumors\\ \vspace{-0.6em} {\footnotesize Final Project for \textit{ECS 171 - Machine Learning} at UC Davis, with Professor Setareh Rafatirad}

### 2025-06-07 latex/draft.tex
added Aryan contributions

Aryan: Aryan completed a literature review and analyzed research papers to identify techniques we can use to address the models overfitting. In the next few weeks Aryan will continue working to improve the models accuracy while also working on documentation and reports.

>>>>

Aryan: Aryan participated in group meetings, worked on literature reviews, helped the group brainstorm ideas and find the dataset, built and deployed the fullstack application, and created the demo video.
